Imprecise Computing in Datapath Design: An Overclocking Approach

### 2013-05-13 TCAD2013/overclocking_tcad.tex
Add Abstract, Modified Figure for Test Framework

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract.
\end{abstract}

\begin{IEEEkeywords}

\end{IEEEkeywords}

@@

The rest of this paper is organized as follows. It first reviews in detail the current literature regarding the existing approaches that are used in word-length optimization and approximate datapath design in Section~\ref{Section_Background}. The analytical error models for two different adder structures: RCA and CSA, are discussed in Section~\ref{section_RCA} and Section~\ref{Section_CSA}, respectively. The decision of the optimum adder structure under the accuracy-performance-area trade-offs, is then put forward in Section~\ref{Section_OptimumAdder}. It is followed by a description of the probabilistic error models for CCM in Section~\ref{section_CCM}. Section.xxx discusses a practical experimental setup to verify our models and test the proposed design methodology. The demonstration of the benefits of our proposed approach is then demonstrated in Section.xxx. Finally, Section.xxx discusses the conclusions of this work and the possible research directions in the future.

@@

\section{Test Platform}\label{Experiment}
In our experiments, we compare two design perspectives. In the first scenario, the word-length of the input signal is truncated before propagating through the datapath in order to meet a given latency. In our proposed overclocking scenario, the circuit is overclocked while keeping the original operand word-length. The benefits of the proposed methodology are demonstrated over a set of DSP example designs, which are implemented on the Xilinx ML605 board with a Virtex-6 FPGA. 
%XC6VLX240T-1FFG1156.

\subsection{Experimental Setup} % (fold)
\label{sub:experimental_setup}
We initially build up a test framework on an FPGA. The general architecture is depicted in Fig.~\ref{Test Framework}. The main body of the test framework consists of the circuit under test (CUT), the test frequency generator and the control logic, as shown in the dotted box in Fig.~\ref{Test Framework}. The I/Os of the CUT are registered by the launch registers (LRs) and the sample registers (SRs), which are all triggered by the test clock. Input test vectors are stored in the on-chip memory during initialization. The results are sampled using Xilinx ChipScope. Finally, we perform an offline comparison of the output of the original circuit at the rated frequency with the output of the overclocked as well as the truncated designs using the same input vectors.
%
\begin{figure}[htbp]
  \centering
  %\vspace{-3.5ex}
  \includegraphics[width=3.3in]{./Figures/TestFramework2.eps}
  %\vspace{-4.5ex}
  \caption{FPGA Test framework, which is composed of a measurement architecture (the dotted box) and an off-line comparator.}
  \label{Test Framework}
  %\vspace{-1ex}
\end{figure}

@@

%In order to avoid the potential timing errors generated from the test framework instead of CUT under high test frequencies, several methods are adopted. Firstly, the control signals for the test frequency generator is triggered by the system clock, which is 33.33MHz in our experiments. This will guarantee that the test clock generation will not be affected by high frequencies. Secondly, since the address counter for the on-chip memory is driven by the test frequency, a deeply pipelined counter structure with initial delay of 258 cycles is used to ensure the correct sample of each address bit. Thirdly, the key internal control signals such as memory address and corresponding operands are recorded together with the outputs to the comparator. Comparisons are performed between these values and the corresponding original values. The results will be discarded if mismatch is found.
% without reimplement the whole design.
% subsection experimental_setup (end)
% \subsection{Experimental Results} % (fold)
% \label{sub:subsubsection_name}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=3.2in]{./Figures/Exp/FIR/RatedFrequency3.eps}
  %\vspace{-1.5ex}
  \caption{The maximum operating frequencies for different input word-lengths of an FIR filter. The dotted line depicts the rated frequency reported by the Xilinx Timing Analyzer. The solid line is obtained through real FPGA tests using our platform.}
  \label{TimingMargin}
  %\vspace{-3.5ex}
\end{figure}

@@

Initially the maximum error-free frequency $f_0$ is applied. In this case we have~(\ref{Eq_decideMu_0}) where $d_c$ is a constant value which denotes the interconnection delay. The frequency is then increased such that~(\ref{Eq_decideMu_1}) is obtained. This process repeats until the maximum frequency $f_{n-1}$ is applied in~(\ref{Eq_decideMu_2}). Based on these frequency values, $\mu$ can be determined.
\begin{eqnarray}\label{Eq_decideMu_0}
\vspace{-1ex}
%\small
%\footnotesize
\scriptsize
  f_0 &= n\mu+d_c
  \vspace{-12ex}
\end{eqnarray}
\vspace{-5ex}
\begin{align}\label{Eq_decideMu_1}
  f_1 &= (n-1)\mu+d_c    \\
  &\cdots               \notag
  \vspace{-3ex}
\end{align}
\vspace{-5.5ex}
\begin{eqnarray}\label{Eq_decideMu_2}
  f_{n-1} &= \mu+d_c
%  \vspace{-2ex}
\end{eqnarray}
\normalsize

\section{Results and Discussion}\label{Section_Experiments}
\subsection{Case study: FIR filter}
We first assess the accuracy of our proposed models of error. The modeled values of both overclocking error and truncation error of the FIR filter are presented in Fig.~\ref{FIR} (dotted lines), as well as the actual measurements on the FPGA (solid lines) with two types of input data. The results demonstrate that our models match well with the practical results obtained using the uniform independent inputs.
% FIR
\begin{figure}[htbp]
  \centering
%  \vspace{-2.5ex}
  \includegraphics[width=3.5in]{./Figures/Exp/FIR/FIR_Error_New_TCAD.eps}
%  \vspace{-5ex}
  \caption{A demonstration of two design perspectives with a $5^{th}$~order FIR filter, which is implemented on Virtex-6 FPGA. The modeled values of both overclocking errors and truncation errors are presented as dotted lines. The actual FPGA measurements are depicted using solid lines. Two types of inputs are employed in the overclocking scenario: the uniformly distributed data and the real image data from Lena.}
  \label{FIR}
%  \vspace{-1ex}
\end{figure}

%Lena image
\begin{figure*}[htbp]
  %\vspace{-2ex}
  \centering
  \subfigure[425MHz,~n=8~,~SNR=47.97dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T8.eps}
  \end{minipage}%
  }% This is important! use % to indicate same line, otherwise new line
  \subfigure[450MHz,~n=8,~SNR=44.94dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T65.eps}
  \end{minipage}
  }%
  \subfigure[480MHz,~n=8,~SNR=21.58dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T62.eps}
  \end{minipage}
  }%
  \subfigure[520MHz,~n=8,~SNR=10.03dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T6.eps}
  \end{minipage}
  }
  \subfigure[425MHz,~n=7,~SNR=26.02dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q7T10.eps}
  \end{minipage}%
  }% This is important! use % to indicate same line, otherwise new line
  \subfigure[450MHz,~n=5,~SNR=21.76dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q4T10.eps}
  \end{minipage}
  }%
  \subfigure[480MHz,~n=2,~SNR=6.57dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q2T10.eps}
  \end{minipage}
  }%
  \subfigure[520MHz,~n=1,~SNR=3.95dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q1T10.eps}
  \end{minipage}
  }
%\vspace{-2ex}
\caption{Output images of the FIR filter for both overclocking scenario (top row) and traditional scenario (bottom row) under various operating frequencies.}
\label{FIR_Lena}
%\vspace{-2ex}
\end{figure*}

@@

\begin{figure}[tbp]
    \begin{minipage}[b]{0.48\textwidth}
        \centering
        \subfigure[The cumulative distribution function with respect to both type of input data.]{
            \centering
            \includegraphics[width=0.95\textwidth]{./Figures/CDF.eps}
            \label{Fig_CSA2stage_Timing}
        }
        \subfigure[Probability distribution of different length of carry chains in the $5^{th}$ order FIR filter, using both type of input data.]{
            \centering
            \includegraphics[width=0.95\textwidth]{./Figures/CC_length2.eps}
            \label{Fig_CSA3stage_Area}
        }
    \end{minipage}
    \centering
    \caption{Statistical analysis of two types of input data: the uniform data and the real image data: Lena.}
\end{figure}

\subsection{Potential Benefits in Circuit Design}
%The results can be interpreted in two folds.
As we mentioned in Section~xxx, our results could be of interest to a circuit designer in two ways. Typically, either the designer will want to create a circuit that can run at a given frequency with the minimum possible MRE, or the algorithm designer will wish to run as fast as possible whilst maintaining a specific error tolerance. For the first design target, the experimental results for all five example designs on FPGA are summarized in Table~\ref{Ratio_MRE} in terms of the relative reduction of MRE as given in~(\ref{Relative Reduction MRE}) where $MRE_{Trad}$ and $MRE_{ovrc}$ denote the value obtained in the traditional scenario and in the overclocking scenario, respectively.

@@

\subsection{Area Overhead}
For both aforementioned design goals, it should be noted that an extra benefit of using the traditional approach is that reducing datapath precision would potentially leads to a smaller design, in comparison to our proposed overclocking scenario. Consequently, the area overheads of our approach are summarized in Table xxx and Table xxx for both design goals. In our experiments, the area overhead is evaluated in terms of the number of LUTs and Slices in the FPGA technology, while similar metrics can also be employed if applying our approach into other hardware platforms. It can be seen that for a given frequency requirement with minimum possible errors, the geometric mean of area overhead ranges from $1.16\times$ and $1.15\times$ to $5.57\times$ and $4.46\times$ for LUTs and Slices, respectively.

An even smaller area overhead can be found for a specified error budget with the maximum clock frequencies. As seen in Table xxx, the geometric mean of area overhead in terms of LUTs and Slices is $1.00\times\sim4.67\times$ and $1.00\times\sim3.70\times$ respectively. Notice that an area overhead of $1\times$ means both the overclocking scenario and the traditional scenario use the original precision, however the former achieves frequency speedups as seen in Tablexxx, because a specific error budget can be tolerated.

@@

\begin{table*}[htbp]
 %% increase table row spacing, adjust to taste
   \renewcommand{\arraystretch}{1.05}
   \setlength{\tabcolsep}{3.5pt}
   \caption{Area Overhead of Our Approach with respect to Given Frequency Requirements}
   \centering
   \footnotesize
   \begin{threeparttable}
   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
     \hline
     \hline
     \multirow{2}*{\begin{tabular}{c}\textbf{Normalized}\\\textbf{Frequency}\end{tabular}} &
     \multicolumn{2}{c|}{\textbf{FIR}} &
     \multicolumn{2}{c|}{\textbf{Sobel}} &
     \multicolumn{2}{c|}{\textbf{IIR}} &
     \multicolumn{2}{c|}{\textbf{Butterworth}} &
     \multicolumn{2}{c||}{\textbf{DCT4}} &
     \multicolumn{2}{c}{\textbf{Geo.Mean}}\\
     &  {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices  }
     &  {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices}\\
     \hline
     1.04 & 1.24	& 1.05  & 1.12 &	1.22 &	 1.26 &	1.42 &	 1.16 &	 1.11 &	 1.13 &	 1.00 & 1.18 & 1.15\\
     1.08 & 1.24	& 1.05	& 1.03 &	1.08 &	 1.26 &	1.42 &	 1.16 &	 1.11 &	 1.11 &	 1.15 & 1.16 & 1.16\\
     1.12 & 1.24	& 1.05   & 1.03 &	1.08 &	 1.26 & 1.42 &	 1.37 &	1.54  &	 2.30 &	 2.17 & 1.38 & 1.40\\
     1.16 & 2.95	& 2.56   & 1.03 &	1.08 &	 1.61 & 1.71 &	 1.99 &	 2.03  &	 4.60 &	 2.89 &2.14 & 1.95\\
     1.20 & 2.95	& 2.56   & 1.66 &	1.39 &	 2.77 &	3.48 &	3.17 &	 3.50  &	 N/A\tnote{*}	  & N/A\tnote{*} & 2.56 & 2.57 \\
     1.24 & 4.42	& 3.15  & 4.00 &	3.55 &	 7.87 &	6.73 &	6.92 &	 5.25  &	 N/A\tnote{*}	  & N/A\tnote{*} & 5.57 & 4.46\\
     1.28 & 4.42	& 3.15   & 4.00 &	3.55 &	 N/A\tnote{*}	    &   N/A\tnote{*}     &	6.92 &	 5.25  &	N/A\tnote{*}	  & N/A\tnote{*} & 4.97& 3.89\\
     1.32 & 4.42	& 3.15   & N/A\tnote{*}	  &	 N/A\tnote{*}	    &	 N/A\tnote{*}	    &	 N/A\tnote{*}   & N/A\tnote{*}   & N/A\tnote{*}    &    N/A\tnote{*}   & N/A\tnote{*} & 4.42	& 3.15 \\
     \hline
     \hline
   \end{tabular}
   \normalsize
   \begin{tablenotes}
   \footnotesize
    \item[*] Current frequency cannot be achieved in the traditional scenario. These points are excluded from the calculation of geometric means.
   \end{tablenotes}
   \end{threeparttable}
   \label{Ratio_MRE}
 \end{table*}

 \begin{table*}[htbp]
 %% increase table row spacing, adjust to taste
   \renewcommand{\arraystretch}{1.05}
   \setlength{\tabcolsep}{3.5pt}
   \caption{Area Overhead of Our Approach with respect to Given Error Budgets.}
   \label{Exp_Real_Inputs}
   \centering
   \footnotesize
   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
     \hline
     \hline
     \multirow{2}*{\begin{tabular}{c}\textbf{Error Budget}\\\textbf{\%}\end{tabular}} &
     \multicolumn{2}{c|}{\textbf{FIR}} &
     \multicolumn{2}{c|}{\textbf{Sobel}} &
     \multicolumn{2}{c|}{\textbf{IIR}} &
     \multicolumn{2}{c|}{\textbf{Butterworth}} &
     \multicolumn{2}{c||}{\textbf{DCT4}} &
     \multicolumn{2}{c}{\textbf{Geo.Mean}} \\
     %\multirow{2}*{\begin{tabular}{c}\textbf{Geo.}\\\textbf{Mean}\end{tabular}}\\
     & {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices }
     & {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices }\\
     \hline
     0.05 & 1.00&	1.00& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00  &1.00  &  1.00\\
     0.5  & 1.02&	1.15& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00   &1.00 &1.03\\
     1    & 1.02&	1.15& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00   &1.00 &1.03\\
     5    & 1.24&	1.05& 1.00&	1.00& 1.26&   1.42&   1.65&   1.11&	 1.00&    1.00   &1.13    &1.11\\
     10   & 1.24&	1.05& 1.12&	1.22& 1.26&	1.42& 1.65&	1.11& 1.11&	 1.15&    1.18    &1.18\\
     20   & 1.24&	1.05& 1.03&	1.08& 1.26&	1.42& 6.92&	 5.25&   3.45&	 2.17   &2.07    &1.79\\
     50   & 2.95&	2.56& 4.00&	3.55& 7.87&	6.73& 6.92&	 5.25&   3.45&	 2.12	&4.67 &3.70\\
     \hline
     \hline
   \end{tabular}
   \normalsize
   \label{Max_Frequency}
 \end{table*}

\section{Conclusion}
The conclusion goes here.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
As process scaling introduces significant performance variations, releasing the tight accuracy requirement rather than covering all possible worst cases would potentially offer the greater freedom to create a design with better performance or energy efficiency. In this paper, we compare two different approaches that could trade accuracy for performance. One is the traditional approach where the precision used in the datapath is limited to meet a target latency. The other is a proposed new approach to boost the clock frequency by simply allowing the datapath to operate without timing closure. We demonstrate analytically and experimentally that on average, our approach obtains either smaller errors or faster operating frequencies in comparison to the traditional approach, since the worst case caused by timing violations only happens rarely, while the precision loss results in errors to all data. We also show that for embedded applications where silicon area is also a limited factor, using the proposed approach on simple arithmetic primitives could achieve better accuracy or performance than using the traditional method on advanced operators.
\end{abstract}

\begin{IEEEkeywords}
Overclocking, Imprecise Computing, Numerical Analysis.
\end{IEEEkeywords}

@@

The rest of this paper is organized as follows. It first reviews in detail the current literature regarding the existing approaches that are used in word-length optimization and approximate datapath design in Section~\ref{Section_Background}. The analytical error models for two different adder structures: RCA and CSA, are discussed in Section~\ref{section_RCA} and Section~\ref{Section_CSA}, respectively. The decision of the optimum adder structure under the accuracy-performance-area trade-offs, is then put forward in Section~\ref{Section_OptimumAdder}. It is followed by a description of the probabilistic error models for CCM in Section~\ref{section_CCM}. Section~\ref{Section_ExpSetup} discusses a practical experimental setup to verify our models and test the proposed design methodology. The demonstration of the benefits of our proposed approach is then demonstrated in Section~\ref{Section_Experiments}. Finally, Section~\ref{Section_Conclusion} discusses the conclusions of this work and the possible research directions in the future.

@@

\section{Test Platform}\label{Section_ExpSetup}
In our experiments, we compare two design perspectives. In the first scenario, the word-length of the input signal is truncated before propagating through the datapath in order to meet a given latency. In our proposed overclocking scenario, the circuit is overclocked while keeping the original operand word-length. The benefits of the proposed methodology are demonstrated over a set of DSP example designs, which are implemented on the Xilinx ML605 board with a Virtex-6 FPGA.
%XC6VLX240T-1FFG1156.

\subsection{Experimental Setup} \label{sub:experimental_setup}
We initially build up a test framework on an FPGA. The general architecture is depicted in Fig.~\ref{Test Framework}. The main body of the test framework consists of the circuit under test (CUT), the test frequency generator and the control logic, as shown in the dotted box in Fig.~\ref{Test Framework}. The I/Os of the CUT are registered by the launch registers (LRs) and the sample registers (SRs), which are all triggered by the test clock. Input test vectors are stored in the on-chip memory during initialization. The results are sampled using Xilinx ChipScope. Finally, we perform an offline comparison of the output of the original circuit at the rated frequency with the output of the overclocked as well as the truncated designs using the same input vectors.
%
\begin{figure}[htbp]
  \centering
  %\vspace{-3.5ex}
  \includegraphics[width=3.5in]{./Figures/TestFramework.pdf}
  %\vspace{-4.5ex}
  \caption{Test framework, which is composed of a measurement architecture (the dotted box) on an FPGA and an off-line comparator using software. Note that the error-free data are obtained by either pre-computation or initial run with low frequencies.}
  \label{Test Framework}
  %\vspace{-1ex}
\end{figure}

@@

%In order to avoid the potential timing errors generated from the test framework instead of CUT under high test frequencies, several methods are adopted. Firstly, the control signals for the test frequency generator is triggered by the system clock, which is much lower than the test frequency. This will guarantee a correct generation of the test clock. Secondly, since the address counter for the on-chip memory is driven by the test frequency, a deeply pipelined counter structure with initial delay of 258 cycles is used to ensure the correct sample of each address bit. Thirdly, the key internal control signals such as memory address and corresponding operands are recorded together with the outputs to the comparator. Comparisons are performed between these values and the corresponding original values. The results will be discarded if mismatch is found.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=3.2in]{./Figures/Exp/FIR/RatedFrequency3.eps}
  %\vspace{-1.5ex}
  \caption{The maximum operating frequencies for different input word-lengths of an FIR filter. The dotted line depicts the rated frequency reported by the timing analysis tool. The solid line is obtained through real FPGA tests using our platform.}
  \label{TimingMargin}
  %\vspace{-3.5ex}
\end{figure}

@@

Initially the maximum error-free frequency $f_0$ is applied. In this case we have~(\ref{Eq_decideMu_0}) where $d_c$ is a constant value which denotes the interconnection delay, and $d_0=1/f_0$. The frequency is then increased such that~(\ref{Eq_decideMu_1}) is obtained. This process repeats until the maximum frequency $f_{n-1}$ is applied in~(\ref{Eq_decideMu_2}). Based on these frequency values, $\mu$ can be determined.

\begin{eqnarray}\label{Eq_decideMu_0}
  %\frac{1}{f_0} &= n\mu+d_c
  d_0 &= n\mu+d_c
  \vspace{-13ex}
\end{eqnarray}
\vspace{-4ex}
\begin{align}\label{Eq_decideMu_1}
  d_1 &= (n-1)\mu+d_c    \\
  &\cdots               \notag
  \vspace{-3ex}
\end{align}
\vspace{-4ex}
\begin{eqnarray}\label{Eq_decideMu_2}
  {d_{n-1}} &= \mu+d_c
\end{eqnarray}

\section{Results and Discussion}\label{Section_Experiments}
\subsection{Case study: FIR filter}
We first assess the accuracy of our proposed models of error. The modeled values of both overclocking error and truncation error of the FIR filter are presented in Fig.~\ref{FIR} (dotted lines), as well as the actual measurements on the FPGA (solid lines) with two types of input data. The results demonstrate that our models match well with the practical results obtained using the uniform independent inputs.
% FIR
\begin{figure}[tbp]
  \centering
%  \vspace{-2.5ex}
  \includegraphics[width=3.5in]{./Figures/Exp/FIR/FIR_Error_New_TCAD.eps}
%  \vspace{-5ex}
  \caption{A demonstration of two design perspectives with a $5^{th}$~order FIR filter, which is implemented on Virtex-6 FPGA. The modeled values of both overclocking errors and truncation errors are presented as dotted lines. The actual FPGA measurements are depicted using solid lines. Two types of inputs are employed in the overclocking scenario: the uniformly distributed data and the real image data from Lena.}
  \label{FIR}
\end{figure}

%Lena image
\begin{figure*}[htbp]
  %\vspace{-2ex}
  \centering
  \subfigure[425MHz,~n=8~,~SNR=47.97dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T8.eps}
  \end{minipage}%
  }% This is important! use % to indicate same line, otherwise new line
  \subfigure[450MHz,~n=8,~SNR=44.94dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T65.eps}
  \end{minipage}
  }%
  \subfigure[480MHz,~n=8,~SNR=21.58dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T62.eps}
  \end{minipage}
  }%
  \subfigure[520MHz,~n=8,~SNR=10.03dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T6.eps}
  \end{minipage}
  }
  \subfigure[425MHz,~n=7,~SNR=26.02dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q7T10.eps}
  \end{minipage}%
  }% This is important! use % to indicate same line, otherwise new line
  \subfigure[450MHz,~n=5,~SNR=21.76dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q4T10.eps}
  \end{minipage}
  }%
  \subfigure[480MHz,~n=2,~SNR=6.57dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q2T10.eps}
  \end{minipage}
  }%
  \subfigure[520MHz,~n=1,~SNR=3.95dB]{
  \begin{minipage}[c]{0.24\textwidth}
    \centering
    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q1T10.eps}
  \end{minipage}
  }
%\vspace{-2ex}
\caption{Output images of the FIR filter for both overclocking scenario (top row) and traditional scenario (bottom row) under various operating frequencies.}
\label{FIR_Lena}
\end{figure*}

@@

In addition, we record the probability distribution of different length of carry chains using an 8-bit RCA with both data types, as shown in Fig.xxx. As the input data is 8-bit, the longest possible carry chain length is 9-bit. It can be observed that when using Lena data,  the probability is only higher for carry chain with a length of 3-bit. While in other situations, using uniform data leads to higher probability, especially for long carry chain length. This finding explicitly demonstrates that longer carry chains happens with an even smaller probability when utilizing real data.

% for short carry chains (i.e. carry chain length of 2-bit or 3-bit),

%In detail, the difference between the two types of data is explicitly

\begin{figure}[tbp]
  \centering
  \includegraphics[width=3.5in]{./Figures/CC_length2.eps}
  \caption{Probability distribution of different length of carry chains in a 8-bit RCA. For the uniform data, two inputs of RCA are randomly sampled from a uniform distribution. For the image data Lena, one input of RCA uses the original data and the other uses the delayed original data for several clock cycles.}
  \label{CarryDistribution}
\end{figure}

%\begin{figure}[tbp]
%    \begin{minipage}[b]{0.48\textwidth}
%        \centering
%        \subfigure[The cumulative distribution function with respect to both type of input data.]{
%            \centering
%            \includegraphics[width=0.95\textwidth]{./Figures/CDF.eps}
%            \label{Fig_CSA2stage_Timing}
%        }
%        \subfigure[Probability distribution of different length of carry chains in the $5^{th}$ order FIR filter, using both type of input data.]{
%            \centering
%            \includegraphics[width=0.95\textwidth]{./Figures/CC_length2.eps}
%            \label{Fig_CSA3stage_Area}
%        }
%    \end{minipage}
%    \centering
%    \caption{Statistical analysis of two types of input data: the uniform data and the real image data: Lena.}
%\end{figure}

\subsection{Potential Benefits in Datapath Design}
%The results can be interpreted in two folds.
As we mentioned in Section~\ref{Section_OptimumAdder}, our results could be of interest to a circuit designer in two ways. Typically, either the designer will want to create a circuit that can run at a given frequency with the minimum possible MRE, or the algorithm designer will wish to run as fast as possible whilst maintaining a specific error tolerance. For the first design target, the experimental results for all five example designs on FPGA are summarized in Table~\ref{Ratio_MRE} in terms of the relative reduction of MRE as given in~(\ref{Relative Reduction MRE}) where $MRE_{Trad}$ and $MRE_{ovrc}$ denote the value obtained in the traditional scenario and in the overclocking scenario, respectively.

@@

\subsection{Area Overhead of Our Approach}
For both aforementioned design goals, it should be noted that an extra benefit of using the traditional approach is that reducing datapath precision would potentially leads to a smaller design, in comparison to our proposed overclocking scenario. Consequently, the area overheads of our approach are summarized in Table~\ref{Table_AreaFrequency} and Table~\ref{Table_AreaError} for both design goals. In our experiments, the area overhead is evaluated in terms of the number of LUTs and Slices in the FPGA technology, while similar metrics can also be employed if applying our approach into other hardware platforms. It can be seen that for a given frequency requirement with minimum possible errors, the geometric mean of area overhead ranges from $1.16\times$ and $1.15\times$ to $5.57\times$ and $4.46\times$ for LUTs and Slices, respectively.

An even smaller area overhead can be found for a specified error budget with the maximum clock frequencies. As seen in Table~\ref{Table_AreaFrequency}, the geometric mean of area overhead in terms of LUTs and Slices is $1.00\times\sim4.67\times$ and $1.00\times\sim3.70\times$ respectively. Notice that an area overhead of $1\times$ means both the overclocking scenario and the traditional scenario use the original precision, however the former achieves frequency speedups as seen in Table~\ref{Table_AreaError}, because a specific error budget can be tolerated.

@@

\begin{table*}[htbp]
 %% increase table row spacing, adjust to taste
   \renewcommand{\arraystretch}{1.05}
   \setlength{\tabcolsep}{3.5pt}
   \caption{Area Overhead of Our Approach with respect to Given Frequency Requirements}
   \label{Table_AreaFrequency}
   \centering
   \footnotesize
   \begin{threeparttable}
   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
     \hline
     \hline
     \multirow{2}*{\begin{tabular}{c}\textbf{Normalized}\\\textbf{Frequency}\end{tabular}} &
     \multicolumn{2}{c|}{\textbf{FIR}} &
     \multicolumn{2}{c|}{\textbf{Sobel}} &
     \multicolumn{2}{c|}{\textbf{IIR}} &
     \multicolumn{2}{c|}{\textbf{Butterworth}} &
     \multicolumn{2}{c||}{\textbf{DCT4}} &
     \multicolumn{2}{c}{\textbf{Geo.Mean}}\\
     &  {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices  }
     &  {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices}\\
     \hline
     1.04 & 1.24	& 1.05  & 1.12 &	1.22 &	 1.26 &	1.42 &	 1.16 &	 1.11 &	 1.13 &	 1.00 & 1.18 & 1.15\\
     1.08 & 1.24	& 1.05	& 1.03 &	1.08 &	 1.26 &	1.42 &	 1.16 &	 1.11 &	 1.11 &	 1.15 & 1.16 & 1.16\\
     1.12 & 1.24	& 1.05   & 1.03 &	1.08 &	 1.26 & 1.42 &	 1.37 &	1.54  &	 2.30 &	 2.17 & 1.38 & 1.40\\
     1.16 & 2.95	& 2.56   & 1.03 &	1.08 &	 1.61 & 1.71 &	 1.99 &	 2.03  &	 4.60 &	 2.89 &2.14 & 1.95\\
     1.20 & 2.95	& 2.56   & 1.66 &	1.39 &	 2.77 &	3.48 &	3.17 &	 3.50  &	 N/A\tnote{*}	  & N/A\tnote{*} & 2.56 & 2.57 \\
     1.24 & 4.42	& 3.15  & 4.00 &	3.55 &	 7.87 &	6.73 &	6.92 &	 5.25  &	 N/A\tnote{*}	  & N/A\tnote{*} & 5.57 & 4.46\\
     1.28 & 4.42	& 3.15   & 4.00 &	3.55 &	 N/A\tnote{*}	    &   N/A\tnote{*}     &	6.92 &	 5.25  &	N/A\tnote{*}	  & N/A\tnote{*} & 4.97& 3.89\\
     1.32 & 4.42	& 3.15   & N/A\tnote{*}	  &	 N/A\tnote{*}	    &	 N/A\tnote{*}	    &	 N/A\tnote{*}   & N/A\tnote{*}   & N/A\tnote{*}    &    N/A\tnote{*}   & N/A\tnote{*} & 4.42	& 3.15 \\
     \hline
     \hline
   \end{tabular}
   \normalsize
   \begin{tablenotes}
   \footnotesize
    \item[*] Current frequency cannot be achieved in the traditional scenario. These points are excluded from the calculation of geometric means.
   \end{tablenotes}
   \end{threeparttable}
   \label{Ratio_MRE}
 \end{table*}

 \begin{table*}[htbp]
 %% increase table row spacing, adjust to taste
   \renewcommand{\arraystretch}{1.05}
   \setlength{\tabcolsep}{3.5pt}
   \caption{Area Overhead of Our Approach with respect to Given Error Budgets.}
   \label{Table_AreaError}
   \centering
   \footnotesize
   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
     \hline
     \hline
     \multirow{2}*{\begin{tabular}{c}\textbf{Error Budget}\\\textbf{\%}\end{tabular}} &
     \multicolumn{2}{c|}{\textbf{FIR}} &
     \multicolumn{2}{c|}{\textbf{Sobel}} &
     \multicolumn{2}{c|}{\textbf{IIR}} &
     \multicolumn{2}{c|}{\textbf{Butterworth}} &
     \multicolumn{2}{c||}{\textbf{DCT4}} &
     \multicolumn{2}{c}{\textbf{Geo.Mean}} \\
     %\multirow{2}*{\begin{tabular}{c}\textbf{Geo.}\\\textbf{Mean}\end{tabular}}\\
     & {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices }
     & {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices }\\
     \hline
     0.05 & 1.00&	1.00& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00  &1.00  &  1.00\\
     0.5  & 1.02&	1.15& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00   &1.00 &1.03\\
     1    & 1.02&	1.15& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00   &1.00 &1.03\\
     5    & 1.24&	1.05& 1.00&	1.00& 1.26&   1.42&   1.65&   1.11&	 1.00&    1.00   &1.13    &1.11\\
     10   & 1.24&	1.05& 1.12&	1.22& 1.26&	1.42& 1.65&	1.11& 1.11&	 1.15&    1.18    &1.18\\
     20   & 1.24&	1.05& 1.03&	1.08& 1.26&	1.42& 6.92&	 5.25&   3.45&	 2.17   &2.07    &1.79\\
     50   & 2.95&	2.56& 4.00&	3.55& 7.87&	6.73& 6.92&	 5.25&   3.45&	 2.12	&4.67 &3.70\\
     \hline
     \hline
   \end{tabular}
   \normalsize
   \label{Max_Frequency}
 \end{table*}

\section{Conclusion}  \label{Section_Conclusion}
The conclusion goes here.
